Meta analysis of reprocessed RNASeq data from AMP-AD for hg38 Reprocessed Data (all 7 brain regions)

### 2022-02-25 code/RNA-Seq_Meta_Analysis.Rmd
update the weights

```{r get.exp}
# Function to read tsv/csv files from synapse
downloadFile <- function(id){ 
  fread(synapser::synGet(id)$path, data.table = F)
}
# Read covariates
covar.ids = c(ROSMAP_DLPFC = 'syn26340637 ', 
              ROSMAP_PCC = 'syn26350606',
              ROSMAP_ACC = 'syn26374583 ',
              MSSM_FP = 'syn26453689', 
              MSSM_IFG = 'syn26454154', 
              MSSM_PHG = 'syn26453943', 
              MSSM_STG = 'syn26454639', 
              MAYO_TCX = 'syn26374583')
#_tissue

all.used.ids = as.character(covar.ids)
covar =  covar.ids %>%
  lapply(downloadFile)
covar$ROSMAP_DLPFC$tissue <- 'DLPFC'
covar$ROSMAP_PCC$tissue <- 'PCC'
covar$ROSMAP_ACC$tissue <- 'ACC'
covar$MSSM_FP$tissue <- 'FP'
covar$MSSM_IFG$tissue <- 'IFG'
covar$MSSM_PHG$tissue <- 'PHG'
covar$MSSM_STG$tissue <- 'STG'
covar$MAYO_TCX$tissue <- 'TCX'

@@

# Read adjusted expression
expr.ids = c(ROSMAP_DLPFC = 'syn26340641', 
              ROSMAP_PCC = 'syn26374587',
              ROSMAP_ACC = 'syn26350610',
              MSSM_FP = 'syn26453693', 
              MSSM_IFG = 'syn26454158', 
              MSSM_PHG = 'syn26453947', 
              MSSM_STG = 'syn26454643', 
              MAYO_TCX = 'syn26387667')

@@

expr =  expr.ids %>%
  lapply(downloadFile) %>%
  plyr::join_all(type = 'full')
```

@@

Weights <- Weights[, c( "ENSG", "Gene", "TE.random", "seTE.random", "fdr.random", 'TE.random.abs', "log_abs_PVal", "Type", "PreAdjWeight", "y" )]
```

>>>>

```{r get.exp}
# Function to read tsv/csv files from synapse
downloadFile <- function(id){ 
  fread(synapser::synGet(id)$path, data.table = F)
}
# Read covariates
#covar.ids = c(ROSMAP_DLPFC = 'syn26340637 ', 
#              ROSMAP_PCC = 'syn26350606',
#              ROSMAP_ACC = 'syn26374583 ',
#              MSSM_FP = 'syn26453689', 
#              MSSM_IFG = 'syn26454154', 
#              MSSM_PHG = 'syn26453943', 
#              MSSM_STG = 'syn26454639', 
#              MAYO_TCX = 'syn26374583')

covar.ids = c(ROSMAP = 'syn26967450 ', 
              MSSM = 'syn27068753', 
              MAYO = 'syn27024950')
#_tissue

all.used.ids = as.character(covar.ids)
covar =  covar.ids %>%
  lapply(downloadFile)
#covar$ROSMAP_DLPFC$tissue <- 'DLPFC'
#covar$ROSMAP_PCC$tissue <- 'PCC'
#covar$ROSMAP_ACC$tissue <- 'ACC'
#covar$MSSM_FP$tissue <- 'FP'
#covar$MSSM_IFG$tissue <- 'IFG'
#covar$MSSM_PHG$tissue <- 'PHG'
#covar$MSSM_STG$tissue <- 'STG'
#covar$MAYO_TCX$tissue <- 'TCX'

@@

# Read adjusted expression
#expr.ids = c(ROSMAP_DLPFC = 'syn26340641', 
#              ROSMAP_PCC = 'syn26374587',
#              ROSMAP_ACC = 'syn26350610',
#              MSSM_FP = 'syn26453693', 
#              MSSM_IFG = 'syn26454158', 
#              MSSM_PHG = 'syn26453947', 
#              MSSM_STG = 'syn26454643', 
#              MAYO_TCX = 'syn26387667')
expr.ids = c(ROSMAP_DLPFC = 'syn26967454', 
              MSSM_STG = 'syn27068759', 
              MAYO_TCX = 'syn27024966')

@@

expr =  expr.ids %>%
  lapply(downloadFile) %>%
  plyr::join_all(type = 'full')
#expr <- as.data.frame(expr) %>%
#  column_to_rownames('feature')

```

@@

Weights <- Weights[, c( "ENSG", "Gene", "TE.random", "seTE.random", "fdr.random", 'TE.random.abs', "log_abs_PVal", "Type", "PreAdjWeight", "y" )]

Weights$plotname <- NA
label_name <- c( "MTCH1", "MTOR", "APPL1", "BAX", "STMN2", "SLC9A9", "TOMM40L", "GABRA2",  "MTCH2"  )
Weights[ Weights$Gene %in% label_name, ]$plotname <- Weights[ Weights$Gene %in% label_name, ]$Gene

A <- Weights[ Weights$Type == 'Actual Rank', ]
row.names(A) <- A$ENSG
colnames(A)[colnames(A)=='PreAdjWeight'] <- 'PreAdjWeight_Actual'
colnames(A)[colnames(A)=='y'] <- 'y_Actual'

B <- Weights[ Weights$Type == 'Predicted Weight', ]
row.names(B) <- B$ENSG
colnames(B)[colnames(B)=='PreAdjWeight'] <- 'PreAdjWeight_Predicted'
colnames(B)[colnames(B)=='y'] <- 'y_Predicted'

plotframe <- as.data.frame(cbind(A[,c('ENSG','Gene', 'TE.random', 'seTE.random', 'fdr.random', 'TE.random.abs', 'log_abs_PVal', 'PreAdjWeight_Actual','y_Actual', 'plotname')], B[row.names(A), c('PreAdjWeight_Predicted','y_Predicted')]))

plotframe <- plotframe[ plotframe$fdr.random < 0.05, ]
plotframe$logTE <- log(abs(plotframe$TE.random.abs))

library(ggplot2)
library(ggrepel)
ggplot2::ggplot(data=plotframe) + 
  ggplot2::geom_point( ggplot2::aes(x=logTE, y=y_Predicted)) +
  ggrepel::geom_label_repel(data = plotframe, 
                            ggplot2::aes(x=logTE, y=y_Predicted, label = plotname, size = NULL, color = NULL),
                            nudge_x = .45,
                            nudge_y = -.05,
                            segment.size  = 0.2,
                            segment.color = "grey50",
                            direction     = "x"
) +
  ggplot2::xlab("Log2( absolute(Effect Size))") + 
  ggplot2::ylab("Assigned weight") +
  ggplot2::labs(title="Weights of Differentially Expressed Transcripts") + 
  ggplot2::theme(plot.title =  ggplot2::element_text(hjust = 0.5))

```
